Visualizations for article

### 2015-12-02 101-visualizations-for-article.Rmd
Pruned version of section by section network graph

```{r}
minimum_n <- 3
top_matches <- 2
codes_not_to_plot <- c("LA1825", "LA1844")

@@

set.seed(4221)
g_n <- g_n %>% add_layout_(with_graphopt(niter = 4000, spring.length = 45),
                           normalize())
par(mar = c(0,0,1,0))
plot(g_n, edge.width = edge_size_clamp(g_n), edge.arrow.size = 0, vertex.size = 5)
```

>>>>

```{r}
minimum_n <- 50
top_matches <- 4
codes_not_to_plot <- c(
  "CO868", 
#   "CT1879", 
  "FL1847", 
  "FL1892", 
  "GA1851",
  "GA1860", 
#   "HI1859", 
#   "HI1897", 
  "IL1866", 
#   "LA1825", 
#   "LA1844", 
#   "MS1848", 
#   "MS1857", 
  "NY1876", 
  "NY1879",
  "VA1860", 
#   "VA1893", 
  "WV1868" 
  )
# codes_not_to_plot <- NULL

@@

set.seed(4221)
g_n <- g_n %>% add_layout_(with_graphopt(niter = 4000, spring.length = 25),
                           normalize())
par(mar = c(0,0,1,0))
plot(g_n, edge.width = edge_size_clamp(g_n), edge.arrow.size = 0, vertex.size = 5)
title("Borrowings between codes, number of sections borrowed")
```
